\begin{itemize}
    \item \textbf{Registration Manager}
        \begin{itemize}
            \item[\text{[R1]}] S\&C allows Students to sign up to the platform through their university credentials using SSO access.
            \item[\text{[R3]}] S\&C allows Companies to sign up to the platform by asking the representative of the company to insert their company email, the VAT number of the company, a Certificate of registration at the Chamber of Commerce, and a letter of authorisation or official assignment signed by a CEO or a HR referent. They have to choose a password.
        \end{itemize}
        
    \item \textbf{Login Manager}
        \begin{itemize}
            \item[\text{[R2]}] S\&C allows Student to login via their university credentials.
            \item[\text{[R4]}] S\&C allows Companies to login to the platform via password and username (created by the system).
        \end{itemize}

        \item \textbf{Profile Manager}
        \begin{itemize}
            \item[\text{[R5]}] S\&C allows Students to upload the PDF of their CV (both for the first time and other times if there have been some changes).
            \item[\text{[R6]}] S\&C allows Students to insert new experiences, skills, and attitudes on their profile.
            \item[\text{[R7]}] S\&C allows Students to edit or delete experiences, skills, and attitudes present on their profile.
        \end{itemize}

        \item \textbf{Adv Manager}
        \begin{itemize}
            \item[\text{[R8]}] S\&C allows Companies to create an advertisement regarding an internship position they are offering, explaining the project of the internship and the terms offered.
            \item[\text{[R9]}] S\&C allows Companies to modify and remove an advertisement posted on their page.
        \end{itemize}

        \item \textbf{Search Manager}
        \begin{itemize}
            \item[\text{[R10]}] S\&C allows Students to use a research bar to find appropriate internship positions by inserting specific requirements about the project and/or the terms offered.
            \item[\text{[R11]}] S\&C allows Companies to use a research bar to find appropriate candidates for their internship positions by inserting specific experiences, skills and/or attitudes the candidates should have.
        \end{itemize}

        \item \textbf{Recommendation Manager}
        \begin{itemize}
            \item [\text{[R12]}] S\&C informs students when an internship that might interest them becomes available.
            \item [\text{[R13]}] S\&C informs companies about the availability of a student whose CV corresponds to their needs. 
        \end{itemize}
        
    \item \textbf{Request Manager}
        \begin{itemize}
            \item [\text{[R14]}] S\&C allows Students to contact a company they are interested in.
            \item [\text{[R15]}] S\&C allows Companies to contact Students they are interested in.
            
        \end{itemize}

        \item \textbf{Inbox Manager}
        \begin{itemize}
            \item [\text{[R16]}] S\&C informs a Student when a Company shows interest in their profile by sending the Student the Company's offer. The Student can accept or decline the offer.
            \item [\text{[R17]}] S\&C informs a Company when a Student shows interest in its offer by sending to the Company the Student's CV, the Company can accept or decline the offer.
            \item [\text{[R18]}] S\&C communicates to Students or Companies if their requests are successful.
        \end{itemize}

        \item \textbf{Match Manager}
        \begin{itemize}
            \item [\text{[R18]}] S\&C communicates to Students or Companies if their requests are successful.
            \item [\text{[R19]}] S\&C allows Companies to setup an interview with the candidates.
        \end{itemize}
        
    \item \textbf{Interview Manager}
        \begin{itemize}
            \item [\text{[R19]}] S\&C allows Companies to setup an interview with the candidates.
            \item [\text{[R20]}] S\&C allows Companies to write a form with all the aspects that will be considered during the interviews.
            \item [\text{[R21]}] S\&C allows Companies to modify or delete the interview form created.
            \item [\text{[R22]}] S\&C allows Companies fill the form during the interview.
        \end{itemize}

        \item \textbf{Feedback Manager}
        \begin{itemize}
            \item [\text{[R23]}] S\&C allows Students to give personal feedback during the selection period about the Company's selection method or during the internship period about the internship itself.
            \item [\text{[R24]}] S\&C allows Companies to give feedback after the interview or during the internship about a single Student.
        \end{itemize}

        \item \textbf{Monitor Manager}
        \begin{itemize}
            \item [\text{[R25]}] S\&C offers Students the possibility to monitor their matchmaking process with a Company (state of the matchmaking, scheduled interview, interview results).
            \item [\text{[R26]}] S\&C offers Companies the possibility to monitor their matchmaking process with a Student.
            \item [\text{[R27]}] S\&C offers Students and Companies the possibility to monitor the state of the internship.
        \end{itemize}
\end{itemize}
